---
title: "An R Interface to OpenWeatherMap"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(testthat)
library(magrittr)
library(owmr)
```

[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/owmr)](https://cran.r-project.org/package=owmr)

`owmr` accesses __OpenWeatherMap's__ API, a service providing weather data in the past, in the future and now and furthermore, serving weather map layers usable in frameworks like `leaflet`. In order to access its API you have to sign up for an API key at

* https://openweathermap.org

## Builds

__master__

[![Travis-CI Build Status](https://travis-ci.org/crazycapivara/owmr.svg?branch=master)](https://travis-ci.org/crazycapivara/owmr)

__develop__

[![Travis-CI Build Status](https://travis-ci.org/crazycapivara/owmr.svg?branch=develop)](https://travis-ci.org/crazycapivara/owmr)

## Installation

```{r installation, eval=FALSE}
# stable
install.packages("owmr")

# unstable
devtools::install_github("crazycapivara/owmr")

# bleeding edge
devtools::install_github("crazycapivara/owmr", ref = "develop")
```

## Introduction

See __OpenWeatherMap's__ API documentation for optional parameters, which can be passed to all functions fetching weather data via the `...` parameter in R

* https://openweathermap.org/api/

### Setup

```{r settings, eval=FALSE}
library(owmr)

# first of all you have to set up your api key
owmr_settings("your_api_key")

# or store it in an environment variable called OWM_API_KEY (recommended)
Sys.setenv(OWM_API_KEY = "your_api_key") # if not set globally
```

### Usage

```{r examples, echo=TRUE, eval=TRUE}
# get current weather data by city name
(res <- get_current("London", units = "metric") %>%
  owmr_as_tibble()) %>% names()
res[, 1:6]

# ... by city id
(rio <- search_city_list("Rio de Janeiro")) %>%
  as.list()

get_current(rio$id, units = "metric") %>%
  owmr_as_tibble() %>% .[, 1:6]

# get current weather for cities around geo point
res <- find_cities_by_geo_point(
  lat = rio$lat,
  lon = rio$lon,
  cnt = 5,
  units = "metric"
) %>% owmr_as_tibble()

idx <- c(names(res[1:6]), "name")
res[, idx]

# get forecast
forecast <- get_forecast("London", units = "metric")
forecast_tbl <- owmr_as_tibble(forecast)

forecast_tbl[, 1:6]

"name: {{name}}, id: {{id}}, (forecast) rows: {{cnt}}" %$$%
  list(
    name = forecast$city$name,
    id   = forecast$city$id,
    cnt  = forecast$cnt
  ) %>% cat()

# apply funcs to some columns
funcs <- list(
  temp = round,
  wind_speed = round
)
forecast_tbl %<>% parse_columns(funcs)

# do some templating ...
("{{dt_txt}}h {{temp}}°C, {{wind_speed}} m/s" %$$%
  forecast_tbl) %>% head(10)
```

## Documentation

* https://crazycapivara.github.io/owmr/

or type

```{r documentation, echo=TRUE, eval=FALSE}
?owmr
```

## Run tests
```{r tests, echo=TRUE, eval=TRUE}
devtools::test()
```
