---
title: "An R Interface to OpenWeatherMap"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(testthat)
library(magrittr)
library(owmr)
```

[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/owmr)](https://cran.r-project.org/package=owmr)

`owmr` accesses __OpenWeatherMap's__ API, a service providing weather data in the past, in the future and now and furthermore, serving weather map layers usable in frameworks like `leaflet`. In order to access its API you have to sign up for an API key at

* https://openweathermap.org

## Builds

__master__

[![Travis-CI Build Status](https://travis-ci.org/crazycapivara/owmr.svg?branch=master)](https://travis-ci.org/crazycapivara/owmr)

__develop__

[![Travis-CI Build Status](https://travis-ci.org/crazycapivara/owmr.svg?branch=develop)](https://travis-ci.org/crazycapivara/owmr)

## Installation

```{r installation, eval=FALSE}
# stable
install.packages("owmr")

# unstable
devtools::install_github("crazycapivara/owmr")

# bleeding edge
devtools::install_github("crazycapivara/owmr", ref = "develop")
```

## Introduction

See __OpenWeatherMap's__ API documentation for optional parameters, which can be passed to all functions fetching weather data via the `...` parameter in R

* https://openweathermap.org/api/

### Setup

```{r settings, eval=FALSE}
library(owmr)

# first of all you have to set up your api key
owmr_settings("your-api-key")

# or store it in an environment variable called OWM_API_KEY (recommended)
Sys.setenv(OWM_API_KEY = "your_api_key") # if not set globally
```

### Usage

```{r examples, echo=TRUE, eval=TRUE}
# get current weather data by city name
(res <- get_current("London", units = "metric") %>%
  flatten()) %>% names()
res[c("coord.lon", "coord.lat", "main.temp", "weather.description")]

# ... by city id
(rio <- search_city_list("Rio de Janeiro")) %>%
  as.list()

get_current(rio$id, units = "metric") %>%
  flatten() %>% .[c("name", "main.temp", "main.humidity", "wind.speed")]

# get forecast
forecast <- get_forecast("London", units = "metric")
names(forecast)

"name: {{name}}, id: {{id}}, (forecast) rows: {{cnt}}" %$$%
  list(
    name = forecast$city$name,
    id   = forecast$city$id,
    cnt  = forecast$cnt) %>% cat()

names(forecast$list)

forecast$list[c("dt_txt", "main.temp", "main.temp_max", "wind.speed")] %>%
  head()

# flatten weather column and tidy up column names
forecast %<>% tidy_up()
names(forecast$list)

# apply funcs to some columns  
forecast$list %<>% parse_columns(list(temp = round, wind_speed = round))

# do some templating ...
("{{dt_txt}}h {{temp}}°C, {{wind_speed}} m/s" %$$%
  forecast$list) %>% head(10)
```

## Documentation

* https://crazycapivara.github.io/owmr/

or type

```{r documentation, echo=TRUE, eval=FALSE}
?owmr
```

## Run tests
```{r tests, echo=TRUE, eval=TRUE}
test_dir("tests/testthat/")
```
